The \dealii{} Library, Version 9.4

### 2022-06-21 9.4/paper.tex
More edits

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class does not output a numerical solution
  on the cells of the original triangulation, but interpolates the result
  onto a second triangulation (which can be completely unrelated).
  By using this class, one can output the result obtained on an
  unstructured mesh on a structured one (which might facilitate a more
  memory-efficient storage format, for example if this second
  triangulation is a uniformly refined rectangle or box), or one can create a slice in 3D.
  \item The new function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows to find the MPI
  rank of the subdomain of a distributed mesh that contains a given point.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. Based on the information obtained,
  the communication pattern used in \texttt{Utilties::MPI::RemotePointEvaluation} can be set up efficiently. Furthermore, this function could be used in the future to allow
  particle simulations where particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction()}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description is applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \item \todo[inline]{Add something about the FEInterfaceValues improvements?}
\end{itemize}
%
The changelog lists more than 175 other features and bugfixes.

@@

  \caption{\it New refinement strategies for triangles and tetrahedra: Triangles
    are subdivided into four children and tetrahedra into eight.
  \todo[inline]{Are these ``new strategies'', or is it ``New:
    Refinement strategies'' because we did not have refinement at all before?}}
  \label{fig:refinement}
\end{figure}

@@

There are now new utility functions in the
\texttt{RepartitioningPolicyTools} namepace that can be
used to create a new \texttt{p::f::T} instance,
given a distributed triangulation (\texttt{p::f::T} or
\texttt{p::d::T}) and a vector that indicates the designated owner processes of locally
owned cells. This approach allows for partitioning \texttt{p::f::T}
based on arbitrary criteria. The workflow is shown in the following listing:
\begin{c++}
// original triangulation:
parallel::distributed::Triangulation<dim> tria(communicator);

@@

In release 9.3~\cite{dealII93}, we added support for global-coarsening multigrid in
addition to the established local-smoothing infrastructure. Global
coarsening smoothens on the whole computational domain on each
multigrid level, which is obtained by coarsening the finest cells of
the next finer multigrid level.
For this purpose, we use a sequence of triangulations, and we perform
the smoothing only on their active levels. To create the sequence of
triangulations, one can use the functions \texttt{MGTransferGlobalCoarseningTools::create\_geometric\_coarsening\_sequence()}. A new version takes an
instance of \texttt{RepartitioningPolicyTools::Base} (see Subsection~\ref{sec:repartitioning}) as argument, which allows to specify the parallel
distribution of each multigrid level (in contrast to the fixed first-child policy in the case of local smoothing). Furthermore, we added support for block vectors,
fixed a number of limitations, and performed performance optimizations of
the transfer operator; particularly, the redundant copy from/to temporary vectors
has been eliminated. Now, hanging-node constraints are applied
efficiently in the same way as in the matrix-free loops (see Subsection~\ref{sec:mf}).

@@

A related function is
\texttt{GridGenerator::surface\_mesh\_to\_volumetric\_mesh()}, which
computes a tetrahedral volume triangulation \texttt{Triangulation<3>}, based on a
given surface triangulation \texttt{Triangulation<2,3>} that bounds
the three dimensional volume.

@@

D.~Wells was supported by NSF through Grant DMS-1344962.

>>>>

While all of these major changes are discussed in detail in
Section~\ref{sec:major}, there
are a number of other noteworthy changes in the current \dealii{} release,
which we briefly outline in the remainder of this section:
%
\begin{itemize}
%  \item \texttt{AffineConstraints::make\_consistent\_in\_parallel()} allows
%  to make constraints consistent in parallel.
  \item The \texttt{DataOutResample} class interpolates values defined on one
  triangulation onto a second potentially unrelated triangulation.
  By using this class, one can output the result obtained on an
  unstructured mesh on a structured one (which might facilitate a more
  memory-efficient storage format, for example if this second
  triangulation is a uniformly refined rectangle or box), or one can create a slice in 3D.
  \item The new member function \texttt{find\_point\_owner\_rank()} of \texttt{parallel::distributed::Triangulation} allows one to find the MPI
  ranks of cells containing specified points.
  It is communication-free and leverages the functionality of p4est (>v.2.2).
  Its algorithm is described in \cite{burstedde2020parallel}. This information
  enables efficient construction of the
  communication pattern used in the class \texttt{Utilties::\allowbreak MPI::\allowbreak RemotePointEvaluation}. Furthermore, this function could be used in the future to allow
  particle simulations in which particle movement is not
  limited by CFL conditions, as done in \cite{mirzadeh2016parallel}.
  \item The new function
  \texttt{GridGenerator::pipe\_junction()}
  generates a triangulation of three cone-shaped pipes that cross at a bifurcation point in any possible configuration.
  A manifold description is applied to the boundary, which can be extended into the volume via transfinite interpolation \cite{Gordon82} using the \texttt{TransfiniteInterpolationManifold} class \cite{dealII90}.
  \item A new DoF renumbering function \texttt{DoFRenumbering::support\_point\_wise()} which groups together
  shape functions by their support point. This functionality is useful in both developing nodal schemes since, e.g., the $x$, $y$, and $z$
  velocities at a point will be consecutive in the solution vector. It also improves interoperability with external libraries which expect
  data in this format.
  \item \todo[inline]{Add something about the FEInterfaceValues improvements?}
\end{itemize}
%
The changelog lists more than 175 other features and bugfixes.

@@

  % We definitely supported tri refinement in 9.3 - see 6ceb8b70559dc2274761a28dc7836f1e9602da8c (Dec 4, 2020)
  % and also 74b8171dd030a4b2de41955b8d913cde06974b91 (Feb 4, 2021)
  \caption{\it New: The previous release \cite{dealII93} added support for adaptive mesh
  refinement with triangles. This release adds support for global tetrahedral refinement.}
  \label{fig:refinement}
\end{figure}

@@

There are now new utility functions in the
\texttt{RepartitioningPolicyTools} namespace that can be
used to create a new \texttt{p::f::T} instance,
given a distributed triangulation (\texttt{p::f::T} or
\texttt{p::d::T}) and a vector that indicates the designated owner processes of locally
owned cells. This approach allows for partitioning \texttt{p::f::T}
based on arbitrary criteria. The workflow is shown in the following listing:
\begin{c++}
// original triangulation:
parallel::distributed::Triangulation<dim> tria(communicator);

@@

In release 9.3~\cite{dealII93}, we added support for global-coarsening multigrid in
addition to the established local-smoothing infrastructure. Global
coarsening smooths on the whole computational domain on each
multigrid level, which is obtained by coarsening the finest cells of
the next finer multigrid level.
For this purpose, we use a sequence of triangulations, and we perform
the smoothing only on their active levels. To create the sequence of
triangulations, one can use the functions \texttt{MGTransferGlobalCoarseningTools::create\_geometric\_coarsening\_sequence()}. A new version takes an
instance of \texttt{RepartitioningPolicyTools::Base} (see Subsection~\ref{sec:repartitioning}) as argument, which allows to specify the parallel
distribution of each multigrid level (in contrast to the fixed first-child policy in the case of local smoothing). Furthermore, we added support for block vectors,
fixed a number of limitations, and performed performance optimizations of
the transfer operator; particularly, the redundant copy from/to temporary vectors
has been eliminated. Now, hanging-node constraints are applied
efficiently in the same way as in the matrix-free loops (see Subsection~\ref{sec:mf}).

@@

A related function is
\texttt{GridGenerator::surface\_mesh\_to\_volumetric\_mesh()}, which
computes a tetrahedral volume triangulation \texttt{Triangulation<3>}, based on a
given surface triangulation \texttt{Triangulation<2,3>} that bounds
the three dimensional shape.

@@

D.~Wells was supported by the NSF Award OAC-1931516.
